\documentclass[12pt,notitlepage]{report}

\title{Aerodynamic Shape Optimization}
\author{Pradu Kannan}
\date{}

\usepackage{math}
\usepackage{nomencl}
\usepackage{titling}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\makenomenclature
\allowdisplaybreaks

\renewcommand{\chaptername}{Section}

\begin{document}

%\begin{titlingpage}
    \maketitle
    \begin{abstract}
        A foray into numerical methods for the direct optimization of aerodynamic shapes.
    \end{abstract}
%\end{titlingpage}
%\maketitle

\tableofcontents
\printnomenclature


\nomenclature{$f:S\to T$}{A function $f$ from set $S$ to set $T$}
\nomenclature{$\N$}{The set of natural numbers $\{0,1,2,\ldots\}$}
\nomenclature{$\R$}{The set of real numbers}
\nomenclature{$\Z$}{The set of integers}
%\nomenclature{$\Q$}{The set of rational numbers}
%\nomenclature{$\Z_+$}{The set of positive integers}
%\nomenclature{$\bar{\Z}_+$}{The set of non-negative integers}
%\nomenclature{$\R_+$}{The set of positive real numbers}
%\nomenclature{$\bar{\R}_+$}{The set of non-negative real numbers}
%\nomenclature{$\C$}{The set of complex numbers}
\nomenclature{$a\in S$}{Element $a$ is member of the set $S$}
\nomenclature{$S\subset T$}{Set $S$ is a proper ($S\neq T$) subset of $T$}
\nomenclature{$S\subseteq T$}{Set $S$ is a subset of $T$}
\nomenclature{$S\times T$}{The cartesian product of set $S$ with $T$.  This is
the set of all ordered pairs $(s,t)$, $s\in S$, $t\in T$.}
\nomenclature{$S^N$}{The cartesian product $S\times S\times S \ldots$ performed
$N$ times.  This is the set of all ordered $N$-tuples $(s_0,s_1,s_2, \ldots
s_{N-1})$.}
\nomenclature{$S \cap T$}{The intersection of sets $S$ and $T$.  All $x$ such that $x\in S$ and $x\in T$.}
\nomenclature{$S \cup T$}{The union of sets $S$ and $T$.  All $x$ such that $x\in S$ or $x\in T$.}
\nomenclature{$S \setminus T$}{The difference of sets. All $x$ such that $x\in S$ and $x\notin T$. }
\nomenclature{$M_{n\times m}(S)$}{The set of $n\times m$ matrices with entries in $S$}
\nomenclature{$M_n(S)$}{The set of $n\times n$ matrices with entries in $S$}
\nomenclature{$A \implies B$}{Proposition $A$ is true implies proposition $B$ is
true. Equivalent to $\neg A \lor B$.}
\nomenclature{$A \iff B$}{Equivalent to $(A \implies B)\land (B \implies A)$.
Written as iff (if and only if).}
\nomenclature{$A \lor B$}{Proposition $A$ is true or proposition $B$ is true.}
\nomenclature{$A \land B$}{Proposition $A$ is true and proposition $B$ is true.}
\nomenclature{$\neg A$}{Proposition $A$ is false.}
\nomenclature{$\forall x P(x)$}{For all $x$ proposition $P(x)$ is true.}
\nomenclature{$\exists x P(x)$}{There exists $x$ such that proposition $P(x)$ is true.}
\nomenclature{$\tp{A}$}{Transpose of matrix $A$.}
\nomenclature{$\ct{A}$}{Conjugate Transpose of matrix $A$.}
\nomenclature{$I_n$}{$n\times n$ identity matrix.}
\nomenclature{$0_n$}{$n\times n$ zero matrix.}
\nomenclature{$0_{n,m}$}{$n\times m$ zero matrix.}
\nomenclature{$\nulset$}{The empty set.}
\nomenclature{$\rho$}{Density}
\nomenclature{$p$}{Pressure}
\nomenclature{$h$}{Specific Enthalpy}
\nomenclature{$T$}{Temperature}
\nomenclature{$t$}{Time}
\nomenclature{$v$}{Velocity}
\nomenclature{$\Tr A$}{Trace of matrix $A$.}
\nomenclature{$\rdel_b \tp{a}$}{Gradient of $a$ with respect to $b$. $\rdel_b \tp{a} = \tp{\left(\pd{a}{b}\right)}$.}
\nomenclature{$a \tp{\ldel_b}$}{Gradient of $a$ with respect to $b$. $a \tp{\ldel_b} = \pd{a}{b}$.}
\nomenclature{$\rdel_b \cdot a$}{Divergence. Also written as $\rdel_b \cdot a = \tp{\rdel_b}a = \tp{a}\ldel_b = a \cdot \ldel_b = \Tr \left( \pd{a}{b} \right)$}
\nomenclature{$\mathcal{S}_2$}{A 2-sphere.  The surface of a sphere embedded in 3D Eucledian space.}
\nomenclature{$\SO(n;F)$}{The Special Orthogonal Lie-Group of dimension $n$ over a field $F$.}


\chapter{Equations of Flow}
\input{eom/main.tex}

\chapter{Numerical Methods and Adaptive Mesh Refinement}
\chapter{PDE Constrained Optimization}

% Bibliography
\newpage
\refstepcounter{chapter}
\addcontentsline{toc}{chapter}{\protect\numberline{\thechapter}Bibliography}
\chaptermark{Bibliography}
\nocite{hinze}
\bibliographystyle{IEEEtran}
\bibliography{main}{}

\end{document}

